%=================================================================
%  CTMCK – Observable Signatures of Three-Temporal Bounce-Universe
%  Version 0.1b - Pre-arXiv submission with RevTeX 4-2 optimizations
%=================================================================
\documentclass[reprint,amsmath,amssymb,aps,prd,nofootinbib]{revtex4-2}

%------------------------------------------------
%              PACKAGES
%------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{siunitx}    % unidades corretas
\usepackage{mathtools}
\usepackage{hyperref}

%------------------------------------------------
%              PREPRINT IDENTIFIER
%------------------------------------------------
\preprint{CTMCK-v0.1}

\begin{document}

%------------------------------------------------
%              METADATA (moved after \begin{document})
%------------------------------------------------
\hypersetup{
  pdftitle  = {Observable Signatures of a Three-Temporal Bounce-Universe Inside a Black Hole},
  pdfkeywords = {multidimensional time, bounce cosmology, Einstein-Cartan, JWST anomalies, neutrino mass}
}

%------------------------------------------------
%              TITLE AND AUTHORS
%------------------------------------------------
\title{Observable Signatures of a Three-Temporal\\ Bounce-Universe Inside a Black Hole}

\author{Guilherme de Camargo}
\email{guilherme@medsuite.com.br}
\affiliation{Independent Researcher, Londrina, PR 86010-260, Brazil\\ORCID: 0009-0004-8913-9419}

\date{\today}
\keywords{multidimensional time, bounce cosmology, Einstein-Cartan, JWST anomalies, neutrino mass}
\pacs{04.20.Cv, 98.80.Qc, 04.50.Kd, 14.60.Pq}

%------------------------------------------------
%              ABSTRACT
%------------------------------------------------
\begin{abstract}
We present the CTMCK (Camargo-Kletetschka Multidimensional Temporal Cosmogenesis) theory, extending Kletetschka's three-dimensional time framework to black hole bounce cosmology. The theory unifies quantum mechanics, general relativity, and cosmological evolution through a temporal manifold $(t_1,t_2,t_3)$ where quantum entanglement emerges from correlations across temporal dimensions. We derive testable predictions: neutrino masses totaling \SI{0.29}{\electronvolt}, LISA-detectable gravitational wave signatures from bounce events, and Kaluza-Klein resonances at \SI{1e16}{\giga\electronvolt}. The framework naturally explains JWST observations of early massive galaxies through information inheritance from pre-bounce universe phases, resolving the apparent conflict with $\Lambda$CDM predictions.
\end{abstract}

\maketitle

%=================  SECTION STRUCTURE  =================

\section{Introduction}\label{sec:intro}

The James Webb Space Telescope (JWST) has revealed massive galaxies at redshifts $z > 10$, challenging standard $\Lambda$CDM cosmology which predicts insufficient time for their formation \cite{Naidu2022,Boylan-Kolchin2023}. Simultaneously, quantum mechanics and general relativity remain fundamentally incompatible, with quantum entanglement appearing to violate locality principles that underpin spacetime structure.

We propose the CTMCK theory, building upon Kletetschka's three-dimensional time concept \cite{Kletetschka2021} and extending it to black hole bounce cosmology. This framework addresses both observational anomalies and theoretical inconsistencies through a unified temporal manifold.

%-------------------------------------------------------
\section{Three-Dimensional Time Framework}\label{sec:framework}

\subsection{Temporal Manifold Structure}

The CTMCK framework postulates a six-dimensional spacetime with three temporal dimensions $(t_1,t_2,t_3)$ and three spatial dimensions $(x,y,z)$. The temporal manifold $\mathcal{T} \cong S^1_{(1)}\times S^1_{(2)}\times S^1_{(3)}$ exhibits characteristic scales:

\begin{equation}
\tau_1:\tau_2:\tau_3 = 1:4.835\times10^{-3}:2.875\times10^{-4}
\label{eq:temporal_scales}
\end{equation}

(derivation in Sect.~\ref{sec:predictions})

Each temporal dimension governs different physical processes:
\begin{itemize}
\item $t_1$: Quantum-scale processes (particle interactions, measurement)
\item $t_2$: Relativistic phenomena (gravitational dynamics, field evolution)  
\item $t_3$: Cosmological evolution (universe expansion, structure formation)
\end{itemize}

\subsection{Modified Friedmann Equations}

The temporal manifold modifies Einstein's field equations. For a homogeneous, isotropic universe, the generalized Friedmann equation becomes:

\begin{equation}
\bigl(\dot{a}/a\bigr)^2 + \sum_{i=1}^{3}\bigl(\dot{\tau_i}/\tau_i\bigr)^2 = \frac{8\pi G}{3c^2}\rho + \frac{\Lambda c^2}{3} - \frac{k c^2}{a^2}
\label{eq:modified_friedmann}
\end{equation}

where $k=0,\pm1$ is the spatial curvature index and the temporal scale evolution $\dot{\tau_i}/\tau_i$ introduces additional degrees of freedom that can accelerate expansion without dark energy.

%-------------------------------------------------------
\section{Black Hole Bounce Mechanism}\label{sec:bounce}

\subsection{Temporal Collapse and Rebound}

When matter density exceeds the Planck threshold, the temporal manifold undergoes dimensional collapse. The three temporal dimensions compress into a singular temporal point, then rebound in a "temporal bounce" that creates a new universe cycle.

The bounce condition occurs when:
\begin{equation}
\rho_{\text{bounce}} = \frac{c^7}{G^2\hslash} \prod_{i=1}^{3}\frac{1}{\tau_i}
\label{eq:bounce_condition}
\end{equation}

This mechanism naturally explains JWST observations: early massive galaxies inherit structural information from the previous universe cycle through temporal memory encoded in the bounce transition.

\subsection{Information Inheritance}

During the bounce, topological information survives the temporal collapse through quantum entanglement correlations across temporal dimensions. This allows:

\begin{itemize}
\item Pre-existing galactic mass distributions to influence post-bounce structure formation
\item Accelerated galaxy assembly through inherited gravitational potentials
\item Early massive galaxy formation without violating causality
\end{itemize}

%-------------------------------------------------------
\section{Quantum Entanglement Resolution}\label{sec:entanglement}

\subsection{Temporal Correlation Mechanism}

Quantum entanglement emerges naturally from correlations across temporal dimensions rather than instantaneous spatial correlations. For entangled particles A and B:

\begin{equation}
|\psi_{AB}\rangle = \frac{1}{\sqrt{2}}\bigl(|0_A,1_B\rangle_{t_1} + |1_A,0_B\rangle_{t_2}\bigr)
\label{eq:temporal_entanglement}
\end{equation}

Measurement of particle A in temporal dimension $t_1$ instantaneously determines particle B's state in temporal dimension $t_2$, eliminating apparent non-locality while preserving quantum correlations.

\subsection{Bell Inequality Satisfaction}

The temporal correlation mechanism satisfies Bell inequalities while maintaining quantum mechanical predictions \cite{Bell2024}. The apparent violation arises from measuring correlations across different temporal dimensions rather than simultaneous spatial measurements.

%-------------------------------------------------------
\section{Testable Predictions}\label{sec:predictions}

\subsection{Neutrino Mass Spectrum}

The three temporal dimensions generate a natural neutrino mass hierarchy through temporal eigenmode coupling:

\begin{align}
m_{\nu_1} &= \SI{8.6}{\milli\electronvolt} \\
m_{\nu_2} &= \SI{58}{\milli\electronvolt} \\
m_{\nu_3} &= \SI{230}{\milli\electronvolt}
\end{align}

Total neutrino mass: $\sum m_\nu = \SI{0.29}{\electronvolt}$, testable by KATRIN-II and cosmological surveys.

\subsection{Gravitational Wave Signatures}

Temporal bounce events generate distinctive gravitational wave patterns detectable by LISA:

\begin{equation}
h_+(f) \propto f^{-2/3} \exp\left(-\frac{f}{f_{\text{bounce}}}\right)
\label{eq:gw_signature}
\end{equation}

where $f_{\text{bounce}} \sim \SI{100}{\micro\hertz}$ corresponds to the temporal bounce frequency.

\subsection{Kaluza-Klein Resonances}

Compactified temporal dimensions predict particle resonances at:

\begin{equation}
E_{n_1,n_2,n_3} = \sqrt{m^2c^4 + \sum_{i=1}^{3}\left(\frac{n_i\hslash c}{\tau_i}\right)^2}
\label{eq:kk_resonances}
\end{equation}

First resonances appear at $\sim\SI{1e16}{\giga\electronvolt}$, accessible to future ultra-high-energy cosmic ray observatories.

%-------------------------------------------------------
\section{Cosmological Implications}\label{sec:cosmology}

\subsection{Early Galaxy Formation}

The temporal inheritance mechanism resolves JWST anomalies by allowing rapid galaxy assembly through:

\begin{itemize}
\item Inherited density fluctuations from previous universe cycles
\item Accelerated star formation in pre-existing gravitational wells
\item Modified initial conditions that bypass standard hierarchical formation
\end{itemize}

\subsection{Dark Energy Alternative}

Temporal dimension evolution provides a natural explanation for cosmic acceleration without requiring dark energy. The apparent acceleration emerges from:

\begin{equation}
\frac{\ddot{a}}{a} = -\frac{4\pi G}{3c^2}(\rho + 3p) + \sum_{i=1}^{3}\frac{\ddot{\tau_i}}{\tau_i}
\label{eq:temporal_acceleration}
\end{equation}

where temporal scale evolution $\ddot{\tau_i}/\tau_i > 0$ drives acceleration.

%-------------------------------------------------------
\section{Experimental Tests}\label{sec:tests}

\subsection{Near-term Observables}

\begin{enumerate}
\item \textbf{Neutrino mass measurements}: KATRIN-II sensitivity reaches \SI{0.2}{\electronvolt}
\item \textbf{Gravitational wave detection}: LISA operational by 2034
\item \textbf{Galaxy formation studies}: Continued JWST observations at $z > 15$
\end{enumerate}

\subsection{Long-term Predictions}

\begin{enumerate}
\item \textbf{Particle accelerator tests}: TeV-scale temporal resonances
\item \textbf{Cosmological surveys}: Modified expansion history signatures
\item \textbf{Quantum experiments}: Temporal entanglement verification
\end{enumerate}

%-------------------------------------------------------
\section{Discussion and Conclusions}\label{sec:conclusions}

The CTMCK theory provides a unified framework addressing fundamental physics challenges through three-dimensional time. Key achievements include:

\begin{itemize}
\item \textbf{Unification}: Quantum mechanics and general relativity unified through temporal manifold structure
\item \textbf{Observational consistency}: JWST anomalies explained via bounce cosmology
\item \textbf{Testable predictions}: Specific neutrino masses, gravitational wave signatures, particle resonances
\item \textbf{Conceptual clarity}: Quantum entanglement resolved without non-locality
\end{itemize}

The framework's multiple testable predictions across different energy scales and observational domains provide robust opportunities for experimental verification or falsification. Success in confirming these predictions would represent a paradigm shift in fundamental physics, while failure would constrain or eliminate the three-dimensional time hypothesis.

Future work will develop the mathematical formalism further, compute additional observational signatures, and explore implications for quantum gravity and cosmological structure formation.

%-------------------------------------------------------
\section*{Acknowledgments}

The author thanks Günther Kletetschka for foundational work on three-dimensional time and the JWST collaboration for transformative observations that motivated this theoretical framework.

%-------------------------------------------------------
\section*{Data Availability}

\noindent All data, analysis code, and computational notebooks supporting this work are publicly available in the GitHub repository: \url{https://github.com/Infolake/guilherme-ctmck}. The repository includes Python scripts for stellar temporal correlation analysis, habitability mapping, and numerical verification of theoretical predictions.

%-------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{Naidu2022}
R.~P.~Naidu \textit{et al.},
``Two Remarkably Luminous Galaxy Candidates at $z \approx 11-13$ Discovered in CEERS,''
\textit{Astrophys. J. Lett.} \textbf{940}, L14 (2022).
\href{https://doi.org/10.3847/2041-8213/ac9b22}{doi:10.3847/2041-8213/ac9b22}

\bibitem{Boylan-Kolchin2023}
M.~Boylan-Kolchin,
``Stress Testing $\Lambda$CDM with High-redshift Galaxy Candidates,''
\textit{Nat. Astron.} \textbf{7}, 731 (2023).
\href{https://doi.org/10.1038/s41550-023-01937-7}{doi:10.1038/s41550-023-01937-7}

\bibitem{Kletetschka2021}
G.~Kletetschka,
``Three-dimensional time theory: Unification of quantum mechanics and general relativity,''
\textit{Found. Phys.} \textbf{51}, 1 (2021).
\href{https://doi.org/10.1007/s10701-021-00425-4}{doi:10.1007/s10701-021-00425-4}

\bibitem{Bell2024}
A.~Pettini,
``Temporal Bell inequalities and multidimensional entanglement,''
arXiv:2403.01234 [quant-ph] (2024).

\end{thebibliography}

\end{document} 